---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wintermovies

<!-- badges: start -->
<!-- badges: end -->

The goal of wintermovies is on the Holiday Movies which has been released between 1929-2023 and how all these holiday movies represent the different holidays of the season such as **Christmas**, **kwanzaa** and **Hanukkah**. 

## Installation

You can install the development version of wintermovies from [GitHub](https://github.com/ETC5523-2024/assignment-4-packages-and-shiny-apps-dulith4/tree/main/wintermovies) with:

```{r, echo=TRUE, message=FALSE, warning=FALSE}
remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-dulith4", subdir = "wintermovies")

```


``` r
# install.packages("pak")
pak::pak("ETC5523-2024/assignment-4-packages-and-shiny-apps-dulith4")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(wintermovies)
data("holiday_movies")
data("cleaned_holiday_movie_genres")
## basic example code
```

The Summary of the Dataset

```{r}
summary(holiday_movies)
summary(cleaned_holiday_movie_genres)
```

## Shiny App

You can also check the Shiny App which is part of the package   

```{r, eval=FALSE}
wintermovies::run_app()
```



